Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-07-24 Paper/paper.tex
Update

\documentclass[fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\usepackage{color}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
\def\lya{Ly$\alpha$~}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{.}{2.7}}
\newcolumntype{e}{D{.}{.}{2.10}}
\newcolumntype{d}{D{.}{.}{2.3}}

@@

\author[Kulkarni et al.]
       {{Girish Kulkarni$^{1,2}$\thanks{Email: kulkarni@ast.cam.ac.uk},
           G\'abor Worseck$^{3}$
           and Joseph F.~Hennawi$^{4}$} \\
         $^1$Institute of Astronomy,
         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
         UK \\
         $^2$Kavli Institute of Cosmology,
         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
         UK \\
         $^2$Institute f\"ur Physik und Astronomie, Universit\"at
         Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, 14476 Potsdam,
         Germany \\
         $^3$Department of Physics, Broida Hall, UC Santa Barbara,
         Santa Barbara, CA 93106-9530, USA}
       \date{Accepted ---. Received ---; in original form ---}

@@

\begin{abstract}
  Determinations of the UV luminosity function of AGN at high
  redshifts are important for constraining the AGN contribution to
  reionization and understanding the growth of supermassive black
  holes.  Recent inferences of the luminosity function suffer from
  inconsistencies arising from inhomogeneous selection and mixing of
  AGN data.  We address this problem by constructing a sample of more
  than 80,000 colour-selected AGN from redshift $z=0$ to $7.5$.  While
  this sample is composed of multiple data sets with spectroscopic
  redshifts and completeness estimates, we homogenise these data sets
  to identical cosmologies, intrinsic AGN spectra, and magnitude
  systems.  Using this sample, we derive the AGN UV luminosity
  function from redshifts $z=0$ to $7.5$.  The luminosity function has
  a double power law form at most redshifts.  The break luminosity
  brightens rapidly with redshift and the faint end of the luminosity
  function steepens.  In spite of this steepening, the contribution of
  AGN to the hydrogen photoionization rate at $z\sim 6$ is
  subdominant, although it can be non-negligible if these luminosity
  functions hold down to $M_{1450}=-18$.  Under reasonable
  assumptions, AGN can reionize \HeII\ by redshift $z=2.9$.  At low
  redshifts ($z<0.5$), AGN can produce about half of the hydrogen
  photoionization rate inferred from the statistics of \HI\ absorption
  lines in the IGM.  Our global analysis of the luminosity function
  also reveals important systematic errors in the data, particularly
  at $z=2.2$--$3.5$, which need to be addressed in future in order to
  improve our results.  We make various fitting functions, luminosity
  function analysis codes, and homogenised AGN data publicly
  available.
\end{abstract}

@@

The luminosity function of active galactic nuclei (AGN) and its
evolution over cosmological time scales has been a matter of central
interest of a large body of work over the last five decades
\citep{1968ApJ...151..393S, 1978A&A....68...17M, 1983ApJ...269..352S,
  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
  2004AJ....128..515F, 2006AJ....131.2766R, 2007ApJ...654..731H,
  2009MNRAS.392...19C, 2010AJ....139..906W, 2011ApJ...728L..26G,
  2013ApJ...773...14R, 2013ApJ...768..105M, 2015AA...578A..83G,
  2015ApJ...798...28K, 2016ApJ...829...33Y, 2016ApJ...833..222J}.
Determination of the AGN luminosity function constrains models of the
build-up of supermassive black holes \citep{1982MNRAS.200..115S,
  2004ApJ...602..603Y, 2007ApJ...654..731H, 2008ApJ...679..118S,
  2009A&A...493...55E, 2000ApJ...531...42H, 2010MNRAS.401.2531A,
  2013ApJ...773...14R, 2014ApJ...787...73D, 2015MNRAS.448.3603D,
  2015MNRAS.452..575S, 2016MNRAS.462..190R}.  Due to the incidence of
supermassive black holes in most galaxies, the tight scaling relations
observed to exist between the mass of these black holes and properties
of their host galaxies, and the increasing consensus that AGN activity
feeds back on the host galaxy evolution, the AGN luminosity function
also constrains models of galaxy formation \citep{2006ApJ...650...42L,
  2008MNRAS.385.1846M}.  Finally, thanks to their relative brightness
and high Lyman-continuum (LyC) escape fractions, the luminosity
function of AGN determines their contribution to the radiation
background that influences the temperature and ionization state of the
intergalactic medium (IGM), possibly even primarily driving hydrogen
and helium reionization in the last twelve billion years
\citep{2012ApJ...746..125H, 2015AA...578A..83G, 2017ApJ...847L..15O,
  2018MNRAS.474.2904P, 2018arXiv180104931P}.

There is a renewed interest in understanding the evolution of the UV
luminosity function of AGN, triggered by the discovery of 19
low-luminosity ($-18.9>M_{1450}>-22.6$) AGN candidates between
redshifts $z=4.1$ and $6.3$ by \citet{2015AA...578A..83G} using a
novel X-ray/NIR selection criterion.  This finding suggested that if
100\% LyC escape fraction is assumed AGN brighter than $M_{1450}=-18$
can potentially produce all of the metagalactic hydrogen
photoionization rate inferred from the \lya forest at $4<z<6$, despite
the fact that these AGN are fainter than the brightest star-forming
galaxies at these redshifts.  (The UV luminosity function of galaxies
at $z=6$ has characteristic magnitude $M^*_{1450}\sim -20$.)  A
significant presence of AGN at high redshift ($z\sim 6$) and a
dominant contribution of AGN to reionization is appealing as the LyC
escape fraction of galaxies is uncertain.  High-redshift galaxies down
to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ ($L\sim
10^{-3}L^*_\mathrm{galaxies}$) at $z=6$ \citep{2017ApJ...835..113L}
and redshifts up to $z=11.1$ \citep{2016ApJ...819..129O} have now been
reported.  But the escape of LyC photons has been measured in only a
few comparatively bright ($L>0.5L^*_\mathrm{galaxies}$) galaxies at
relatively low redshifts ($z < 4$).  The escape fraction in these
galaxies reveals a broad distribution from less than 2\% to more than
80\% \citep{2010ApJ...725.1011V, 2011ApJ...736...41B,
  2015ApJ...804...17S, 2015ApJ...810..107M, 2016A&A...585A..48G,
  2017MNRAS.468..389J, 2018arXiv180506071S, 2018arXiv180601741F,
  2018arXiv180511621M, 2018arXiv180303655C}, but the average escape
fraction is typically lower than 20\%.  Statistical constraints from
\HI\ column density measurements in gamma-ray burst (GRB) afterglow
spectra suggest an even lower escape fraction of 0.5\%
\citep{2007ApJ...667L.125C, 2009ApJS..185..526F, 2018arXiv180507318T}.
This is a challenge for reionization models, which require an escape
fraction of about 20\% in galaxies as faint as $M_\mathrm{UV}=-13$
\citep{2016PASA...33...37F, 2015ApJ...802L..19R, 2016MNRAS.457.4051K}.
An enhanced incidence of high-redshift AGN may also be consistent with
the shallow bright-end slopes of the $z\sim 7$ UV luminosity function
of galaxies relative to a Schechter function
\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
  2015MNRAS.452.1817B} and the hard spectra of these galaxies
\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S}.
Finally, AGN may also provide a natural explanation for the large
scatter in the \lya opacity between different quasar sightlines close
to redshift $z=6$ \citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
These opacity fluctuations extend to substantially larger scales
($\gtrsim 50\, h^{-1}$cMpc) than expected in galaxies-dominated
reionization models (\citealt{2015MNRAS.453.2943C}; although see
\citealt{2016MNRAS.460.1328D, 2015ApJ...813L..38D,
  2018arXiv180308932B}).  AGN clustering can result in these
fluctuations naturally if there is a significant contribution
($\gtrsim 50\%$) of AGN to the ionising emissivity at $z=5$--$6$
\citep{2017MNRAS.465.3429C}.

Several counter-arguments against a higher incidence of AGN at high
redshift have also been made. \citet{2017MNRAS.468.4691D} and
\citet{2018MNRAS.473.1416M} pointed out that an enhanced number
density of AGN at $z\sim 6$ can lead to a much earlier
\HeII\ reionization (see also \citealt{2017MNRAS.471..255K}).  For
instance, He~\textsc{ii} reionization is complete at $z=4.5$ in the
model of \citet{2015ApJ...813L...8M}, compared to $z=3$ in the
standard scenario \citep{2012ApJ...746..125H}.  Such early
\HeII\ reionization will also result in higher IGM temperatures due to
the associated photoheating.  \citet{2017MNRAS.468.4691D} found that
the temperature of the IGM at mean density is twice as much in
AGN-dominated reionization models as the standard models at
$z=3.5$--$5$, in conflict with constraints from the \lya forest.  This
inconsistency could be avoided by postulating a reduced escape
fraction of \HeII-ionizing photons in AGN, but it is difficult to
reconcile this with a unit escape fraction of hydrogen-ionizing
photons that is required to explain the Ly$\alpha$ opacity
fluctuations.  Further arguments against AGN-dominated reionization
have been presented by \citet{2016MNRAS.459.2299F}, who analysed the
simulations of metal-line absorbers at $z\sim 6$.
\citet{2016MNRAS.459.2299F} find that in their cosmological radiation
hydrodynamical simulations AGN-dominated UV background results in too
many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
C~\textsc{ii} at $z\sim 6$.  (However, note that these simulations
assume a $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
\citep{2002ApJ...565..773T}, which is somewhat harder than recent
measurements ($L_\nu\propto\nu^{-1.7}$) by
\citet{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} found that,
relative to the the standard model \citep{2012ApJ...746..125H}, the
observed N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
measurements seem to require a harder and more intense $>4$~Ry
background.)  Finally, comparing the \citet{2015AA...578A..83G} sample
to X-ray-selected quasar data at $z=0$--$6$,
\citet{2017MNRAS.465.1915R} argued that the faint end of the AGN UV
luminosity function at $z\sim 6$ is probably shallower that that
reported by \citet{2015AA...578A..83G}.  \citet{2017MNRAS.465.1915R}
argue that the apparent contradiction with the results of
\citet{2015AA...578A..83G} could be explained by contamination from
the host galaxies for faint AGN \citep[see
  also][]{2015MNRAS.453.1946G,2015MNRAS.448.3167W,2016MNRAS.463..348V}.

A straightforward way towards a more robust understanding of AGN
contribution to UV background is to determine the evolution of the AGN
UV luminosity function.  To this end, several estimates of the
luminosity function at various redshifts have been published in the
last decade \citep{2009A&A...507..781S, 2011ApJ...728L..26G,
  2012ApJ...755..169M, 2013ApJ...773...14R, 2013ApJ...768..105M,
  2015AA...578A..83G, 2016ApJ...833..222J, 2016ApJ...829...33Y,
  2017ApJ...847L..15O, 2018PASJ...70S..34A}.  However, many of these
inferences of the luminosity function suffer from inconsistencies
arising from inhomogeneous selection and mixing of AGN data.  Some of
the data sets analysed in these studies consist of photometric
samples, which is likely to increase sample contamination.  In some
studies, distinct data sets binned differently in redshift and
magnitudes were inhomogeneously combined.  Some authors imposed
restricted priors on parameters while fitting luminosity function
models, e.g., by fixing luminosity function slopes to certain values,
which may bias the result.  Finally, some studies arbitrarily excluded
certain data sets.  This has resulted in a large scatter in the
inferred high-redshift hydrogen-ionizing AGN emissivity between
various recent studies.  For instance, there is an order of magnitude
scatter between various estimates of the hydrogen-ionizing AGN
emissivity at $z=5$--$6$ \citep{2011ApJ...728L..26G,
  2012ApJ...755..169M, 2015AA...578A..83G, 2018PASJ...70S..34A,
  2018AJ....155..131M, 2018MNRAS.474.2904P, 2017ApJ...847L..15O}.  Our
aim in this paper is to address this issue, by constructing an AGN
sample with robust redshift and completeness estimates and homogeneous
assumptions of the cosmology and intrinsic AGN spectrum.  After
constructing such a sample, we derive the UV luminosity function of
AGN from redshift $z=0$--$7$ and estimate the AGN contribution to the
UV background.  We discuss our sample construction in
Section~\ref{sec:sample}.  Our derived luminosity functions are
presented in Section~\ref{sec:lf}.  Section~\ref{sec:reion} presents
our inference of the AGN contribution to hydrogen and helium
reionization.  We summarise our findings in Section~\ref{sec:conc}.

@@

\section{Homogenised Quasar Sample}
\label{sec:sample}

@@

After homogenising the samples and selection functions we are in a
position to compute the UV luminosity function of AGN. We begin our
analysis by computing binned estimates of the luminosity function as a
function of magnitude in several redshift intervals.  We then perform
parametric maximum-likelihood fits of the luminosity function in the
individual redshift bins, examine the resulting parameters as a
function of redshift, and attempt a joint fit in magnitude and
redshift.  For simplicity we will use the notation $M\equiv M_{1450}$
in the following.

@@

From Figure~\ref{fig:mosaic} we see that the distribution of luminosity
function values in each redshift bin are suggestive of a double power
law form for the QLF.  We will fit such a form below. 
However, in several redshift bins we note a suspicious decline of the
luminosity function at the faint limit of several surveys, for example in
the 2SLAQ sample at $z<2.2$, and in the SDSS sample at $z<1.8$ and $z\sim 4$.
The inconsistency between the SDSS faint end and the deeper
2SLAQ QLF indicates that the SDSS selection function is
systematically overestimated at its magnitude limit.
At $z\sim 4$ the SDSS faint end QLF is inconsistent with the fainter
\citet{2011ApJ...728L..26G} QLF. We identify such discrepant bins
`by eye', discard the contributing quasars from our analysis, and set their
selection function values to zero.
The discarded magnitude bins are shown in Figure~\ref{fig:mosaic} by
open circles.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_individuals.pdf}
    % summary_bins.py 
  \end{center}
  \caption{Redshift evolution of the four double power law parameters
    from the redshift bins shown in Figure~\ref{fig:mosaic}.  Vertical
    error bars show one-sigma (68.26\%) statistical uncertainties,
    whereas horizontal error bars show widths of the redshift bins.
    We identify the general evolutionary trends of each of these
    parameters from the bins shown by the filled symbols.  The open
    symbols show bins that appear to be offset from these trends,
    likely due to unknown systematic errors.  The open circles at
    $2.2<z<3.5$ show the BOSS sample, while the bins at $z < 0.6$
    contain AGN from the SDSS and 2SLAQ data sets.  See
    Section~\ref{sec:bins} for further details.}
  \label{fig:evoln}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    models.  The symbols show the posterior median values of
    parameters with one-sigma (68.26\%) uncertainties in redshift bins
    from Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected
    by systematics and removed from the global analysis are shown in
    grey.  In each panel, the solid curves and shaded regions show the
    three derived global models with one-sigma uncertainties.  Model~1
    provides a better fit, but requires a rapid change in the
    faint-end slope at $z\sim 3.5$.}
  \label{fig:evoln_global}
\end{figure*}

>>>>

\documentclass[fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{.}{2.7}}
\newcolumntype{e}{D{.}{.}{2.10}}
\newcolumntype{d}{D{.}{.}{2.3}}

@@

\author[Kulkarni et al.]
       {{Girish Kulkarni$^{1,2}$\thanks{Email: kulkarni@ast.cam.ac.uk},
           G\'abor Worseck$^{3,5}$
           and Joseph F.~Hennawi$^{4,5}$} \\
         $^1$Institute of Astronomy,
         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
         UK \\
         $^2$Kavli Institute of Cosmology,
         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
         UK \\
         $^2$Institut f\"ur Physik und Astronomie, Universit\"at
         Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, D-14476 Potsdam,
         Germany \\
         $^4$Department of Physics, Broida Hall, UC Santa Barbara,
         Santa Barbara, CA 93106-9530, USA\\
         $^5$Max Planck Institute for Astronomy, K\"onigstuhl 17,
         D-69117 Heidelberg, Germany}
       \date{Accepted ---. Received ---; in original form ---}

@@

\begin{abstract}
  Determinations of the UV luminosity function of AGN at high
  redshifts are important for constraining the AGN contribution to
  reionization and understanding the growth of supermassive black
  holes.  Recent inferences of the luminosity function suffer from
  inconsistencies arising from inhomogeneous selection and mixing of
  AGN data.  We address this problem by constructing a sample of more
  than 80,000 colour-selected AGN from redshift $z=0$ to $7.5$.  While
  this sample is composed of multiple data sets with spectroscopic
  redshifts and completeness estimates, we homogenise these data sets
  to identical cosmologies, intrinsic AGN spectra, and magnitude
  systems.  Using this sample, we derive the AGN UV luminosity
  function from redshifts $z=0$ to $7.5$.  The luminosity function has
  a double power law form at all redshifts.  The break magnitude
  brightens rapidly with redshift and the faint end of the luminosity
  function steepens.  In spite of this steepening, the contribution of
  AGN to the hydrogen photoionization rate at $z\sim 6$ is
  subdominant, although it can be non-negligible if these luminosity
  functions hold down to $M_{1450}=-18$.  Under reasonable
  assumptions, AGN can reionize \HeII\ by redshift $z=2.9$.  At low
  redshifts ($z<0.5$), AGN can produce about half of the hydrogen
  photoionization rate inferred from the statistics of \HI\ absorption
  lines in the IGM.  Our global analysis of the luminosity function
  also reveals important systematic errors in the data, particularly
  at $z=2.2$--$3.5$, which need to be addressed in future in order to
  improve our results.  We make various fitting functions, luminosity
  function analysis codes, and homogenised AGN data publicly
  available.
\end{abstract}

@@

The luminosity function of active galactic nuclei (AGN) and its
evolution over cosmological time scales has been a matter of central
interest of a large body of work over the last five decades
\citep{1968ApJ...151..393S, 1978A&A....68...17M, 1983ApJ...269..352S,
  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
  2004AJ....128..515F, 2006AJ....131.2766R, 2007ApJ...654..731H,
  2009MNRAS.392...19C, 2010AJ....139..906W, 2011ApJ...728L..26G,
  2013ApJ...773...14R, 2013ApJ...768..105M, 2015AA...578A..83G,
  2015ApJ...798...28K, 2016ApJ...829...33Y, 2016ApJ...833..222J}.
Determination of the AGN luminosity function constrains models of the
build-up of supermassive black holes \citep{1982MNRAS.200..115S,
  2004ApJ...602..603Y, 2007ApJ...654..731H, 2008ApJ...679..118S,
  2009A&A...493...55E, 2000ApJ...531...42H, 2010MNRAS.401.2531A,
  2013ApJ...773...14R, 2014ApJ...787...73D, 2015MNRAS.448.3603D,
  2015MNRAS.452..575S, 2016MNRAS.462..190R}.  Due to the incidence of
supermassive black holes in most galaxies, the tight scaling relations
observed to exist between the mass of these black holes and properties
of their host galaxies, and the increasing consensus that AGN activity
feeds back on the host galaxy evolution, the AGN luminosity function
also constrains models of galaxy formation \citep{2006ApJ...650...42L,
  2008MNRAS.385.1846M}.  Finally, thanks to their brightness and high
Lyman-continuum (LyC) escape fractions, the luminosity function of AGN
determines their contribution to the ultraviolet background that
governs the temperature and ionization state of the intergalactic
medium (IGM), possibly even primarily driving hydrogen and helium
reionization 
\citep{2012ApJ...746..125H, 2015AA...578A..83G, 2017ApJ...847L..15O,
  2018MNRAS.474.2904P, 2018arXiv180104931P}.

There is a renewed interest in understanding the evolution of the UV
luminosity function of AGN, triggered by the discovery of 19
low-luminosity ($-18.9>M_{1450}>-22.6$) AGN candidates between
redshifts $z=4.1$ and $6.3$ by \citet{2015AA...578A..83G} using a
novel X-ray/NIR selection criterion.  This finding suggested that AGN
brighter than $M_{1450}\sim -18$ can account for all of the
metagalactic hydrogen photoionization rate inferred from the \lya
forest at $4<z<6$, despite the fact that these AGN are fainter than
the brightest star-forming galaxies at these redshifts.  (The UV
luminosity function of galaxies at $z=6$ has characteristic magnitude
$M^*_{1450}\sim -20$.)  A significant presence of AGN at high redshift
($z\sim 6$) and a dominant contribution of AGN to reionization is
appealing as the LyC escape fraction of galaxies is uncertain, whereas
for AGN it is close to 100\% \citep{2014ApJ...794...75S,
  2015MNRAS.449.4204L, 2016A&A...585A..48G}.  High-redshift galaxies
down to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ at $z=6$
\citep{2017ApJ...835..113L} and redshifts up to $z=11.1$
\citep{2016ApJ...819..129O} have now been reported.  But the escape of
LyC photons has been measured in only a few comparatively bright
($L>0.5L^*_\mathrm{galaxies}$) galaxies at relatively low redshifts
($z < 4$).  The escape fraction in these galaxies reveals a broad
distribution from less than 2\% to more than 80\%
\citep{2010ApJ...725.1011V, 2011ApJ...736...41B, 2015ApJ...804...17S,
  2015ApJ...810..107M, 2016A&A...585A..48G, 2017MNRAS.468..389J,
  2018arXiv180506071S, 2018arXiv180601741F, 2018arXiv180511621M,
  2018arXiv180303655C}, but the average escape fraction is typically
lower than 20\%.  Statistical constraints from \HI\ column density
measurements in gamma-ray burst (GRB) afterglow spectra suggest an
even lower escape fraction of 0.5\% \citep{2007ApJ...667L.125C,
  2009ApJS..185..526F, 2018arXiv180507318T}.  This is a challenge for
reionization models, which require an escape fraction of about 20\% in
galaxies as faint as $M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F,
  2015ApJ...802L..19R, 2016MNRAS.457.4051K}.  An enhanced incidence of
high-redshift AGN may also be consistent with the shallow bright-end
slopes of the $z\sim 7$ UV luminosity function of galaxies relative to
a Schechter function \citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B,
  2014ApJ...792...76B, 2015MNRAS.452.1817B} and the hard spectra of
these galaxies \citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S,
  2017MNRAS.464..469S}.  Finally, AGN may also provide a natural
explanation for the large scatter in the \lya opacity between
different quasar sightlines close to redshift $z=6$
\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.  These opacity
fluctuations extend to substantially larger scales ($\gtrsim 50\,
h^{-1}$cMpc) than expected in galaxy-dominated reionization models
(\citealt{2015MNRAS.453.2943C}; although see
\citealt{2016MNRAS.460.1328D, 2015ApJ...813L..38D,
  2018arXiv180308932B}).  AGN clustering can result in these
fluctuations naturally if there is a significant contribution
($\gtrsim 50\%$) of AGN to the ionising emissivity at $z=5$--$6$
\citep{2017MNRAS.465.3429C}.

Several counter-arguments against a higher incidence of AGN at high
redshift have also been made. \citet{2017MNRAS.468.4691D} and
\citet{2018MNRAS.473.1416M} pointed out that an enhanced number
density of AGN at $z\sim 6$ can lead to a much earlier
\HeII\ reionization (see also \citealt{2017MNRAS.471..255K}).  For
instance, He~\textsc{ii} reionization is complete at $z=4.5$ in the
model of \citet{2015ApJ...813L...8M}, compared to $z=3$ in the
conventional scenario with sharply dropping AGN emissivity at $z>2$
\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization will also
result in higher IGM temperatures due to the associated photoheating.
\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
mean density is twice as much in AGN-dominated reionization models as
the standard models at $z=3.5$--$5$, in conflict with constraints from
the \lya forest.  This inconsistency could be avoided by postulating a
reduced escape fraction of \HeII-ionizing photons in AGN, but it is
difficult to reconcile this with a unit escape fraction of
hydrogen-ionizing photons that is required to explain the Ly$\alpha$
opacity fluctuations.  Further arguments against AGN-dominated
reionization have been presented by \citet{2016MNRAS.459.2299F}, who
analysed the simulations of metal-line absorbers at $z\sim 6$.
\citet{2016MNRAS.459.2299F} find that in their cosmological radiation
hydrodynamical simulations AGN-dominated UV background results in too
many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
C~\textsc{ii} at $z\sim 6$.  Finally, comparing the
\citet{2015AA...578A..83G} sample to X-ray-selected quasar data at
$z=0$--$6$, \citet{2017MNRAS.465.1915R} argued that the faint end of
the AGN UV luminosity function at $z\sim 6$ is probably shallower that
that reported by \citet{2015AA...578A..83G}.
\citet{2017MNRAS.465.1915R} argue that the apparent contradiction with
the results of \citet{2015AA...578A..83G} could be explained by
contamination from the host galaxies for faint AGN \citep[see
  also][]{2015MNRAS.453.1946G,2015MNRAS.448.3167W,2016MNRAS.463..348V}.

The premier way towards a more robust understanding of the AGN
contribution to the UV background is to determine the evolution of the
AGN UV luminosity function across cosmic time.  To this end, numerous
measurements of the luminosity function at various redshifts have been
published in the last decade \citep{2009A&A...507..781S,
  2011ApJ...728L..26G, 2012ApJ...755..169M, 2013ApJ...773...14R,
  2013ApJ...768..105M, 2015AA...578A..83G, 2016ApJ...833..222J,
  2016ApJ...829...33Y, 2017ApJ...847L..15O, 2018PASJ...70S..34A}.
However, many of these inferences suffer from inconsistencies arising
from inhomogeneous selection and mixing of AGN data.  Some of the data
sets analysed in these studies consist of photometric samples, which
is likely to increase sample contamination.  In some studies, distinct
data sets binned differently in redshift and magnitudes were
inhomogeneously combined.  Some authors imposed restricted priors on
parameters while fitting luminosity function models, e.g., by fixing
luminosity function slopes to certain values, which may bias the
result.  Finally, some studies arbitrarily excluded certain data sets.
This has resulted in a large scatter in the inferred high-redshift
hydrogen-ionizing AGN emissivity between various recent studies.  For
instance, there is an order of magnitude scatter between various
estimates of the hydrogen-ionizing AGN emissivity at $z=5$--$6$
\citep{2011ApJ...728L..26G, 2012ApJ...755..169M, 2015AA...578A..83G,
  2018PASJ...70S..34A, 2018AJ....155..131M, 2018MNRAS.474.2904P,
  2017ApJ...847L..15O}.  Our aim in this paper is to address this
issue, by constructing an AGN sample with robust redshift and
completeness estimates and homogeneous assumptions of the cosmology
and intrinsic AGN spectrum.  After constructing such a sample, we
derive the UV luminosity function of AGN from redshift $z=0$--$7.5$
and estimate the AGN contribution to the UV background.  We discuss
our sample construction in Section~\ref{sec:sample}.  Our derived
luminosity functions are presented in Section~\ref{sec:lf}.
Section~\ref{sec:reion} presents our inference of the AGN contribution
to the \nHI-ionizing UV background and \HeII\ reionization history.
We summarise our findings in Section~\ref{sec:conc}.

@@

\section{Homogenised AGN Sample}
\label{sec:sample}

@@

After homogenising the samples and selection functions we are in a
position to compute the UV luminosity function of AGN. We begin our
analysis by computing binned estimates of the luminosity function as a
function of magnitude in several narrow redshift intervals.  We then
perform parametric maximum-likelihood fits of the luminosity function
in the individual redshift bins, examine the resulting parameters as a
function of redshift, and attempt a joint fit in magnitude and
redshift.  For simplicity we will use the notation $M\equiv M_{1450}$
in the following.

@@

From Figure~\ref{fig:mosaic} we see that the distribution of
luminosity function values in each redshift bin are suggestive of a
double power law form for the QLF.  We will fit such a form below.
However, in several redshift bins we note a suspicious decline of the
luminosity function at the faint limit of several surveys, for example
in the 2SLAQ sample at $z<2.2$, and in the SDSS sample at $z<1.8$ and
$z\sim 4$.  The inconsistency between the SDSS faint end and the
deeper 2SLAQ QLF indicates that the SDSS selection function is
systematically overestimated at its magnitude limit.  At $z\sim 4$ the
SDSS faint end QLF is inconsistent with the fainter
\citet{2011ApJ...728L..26G} QLF. We identify such discrepant bins by
eye, discard the contributing quasars from our analysis, and set their
selection function values to zero.  The discarded magnitude bins are
shown in Figure~\ref{fig:mosaic} by open circles.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_individuals.pdf}
    % summary_bins.py 
  \end{center}
  \caption{Redshift evolution of the four double power law parameters
    from the redshift bins shown in Figure~\ref{fig:mosaic}.  Vertical
    error bars show one-sigma (68.26\%) statistical uncertainties
    derived from the posterior distribution, whereas horizontal error
    bars show widths of the redshift bins.  We identify the general
    evolutionary trends of each of these parameters from the bins
    shown by the filled symbols.  The open symbols show bins that
    appear to be offset from these trends, likely due to 
    systematic errors.  The open circles at $2.2<z<3.5$ show the BOSS
    sample, while the bins at $z < 0.6$ contain AGN from the SDSS and
    2SLAQ data sets.}
  \label{fig:evoln}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    models.  The symbols show the posterior median values of
    parameters with one-sigma (68.26\%) uncertainties in redshift bins
    from Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected
    by systematics and removed from the global analysis are shown by
    the grey open circles.  In each panel, the solid curves and shaded
    regions show the three derived global models with one-sigma
    uncertainties.  Model~1 provides a better fit, but requires a
    rapid change in the faint-end slope at $z\sim 3.5$.}
  \label{fig:evoln_global}
\end{figure*}
